Modular transmission line probes for microfluidic nuclear magnetic resonance spectroscopy and imaging

### 2018-12-19 ms5n17-tlp-mn-180216-001.tex
New figures

\title{Modular transmission line probes for microfluidic NMR}

@@

Microfluidic NMR (Nuclear Magnetic Resonance) presents the possibility of probing chemical or bio-chemical reactions, cells, and tissues non-invasively in a tightly controlled and tailored microfluidic environment. We present a dual channel modular probe assembly for  high efficiency microfluidic-NMR. The samples are contained in exchangeable, flow compatible planar microfluidic devices. The detector including the tuning and matching circuitry of the probe is modular which allows the use of different detectors optimised for different experimental conditions on the same probe base. The probe body is made from prefabricated aluminium profiles and few precision machined parts, while the probe circuit and detector are made from PCB materials. The probe can be built from scratch with no requirement of any parts or electronics from commercial probes. The probe has a limit of detection of 1.18 nmol s$^{-1/2}$ and excellent B$_{1}$ homogeneity. The probe is optimised for proton detection and can be tuned and matched simultaneously to proton and X channel ($^{13}$C or $^{15}$N) frequencies. We have successfully acquired $^1$H-$^{13}$C and $^1$H-$^{15}$N heteronuclear correlation spectrum (HSQC). Particularly, $^1$H-$^{15}$N HSQC spectrum of 1 mM $^{15}$N labeled ubiquitin from 2.5 $\mu$l of sample volume.

@@

%\clearpage

@@

NMR (Nuclear Magnetic Resonance) is a well established technique used in chemical analysis~\cite{NMR-chemical-1995, hills1994magnetic, rabenstein1991quantitative}, metabolomics~\cite{nmr-metabolomics-future-2017,nmr-metabolomics-2016}, molecular structure determination~\cite{wuthrich1990protein}, reaction monitoring~\cite{maiwald2004quantitative} etc. Microfluidic lab-on-a-chip (LOC) devices are increasingly finding wide applications in chemistry and the life sciences~\cite{whitesides2006origins,mark2010microfluidic}. In addition to providing a way to integrate complex chemical and biochemical analytical processes with sample preparation and even culture of cells and other biological systems, they allow detailed control over growth conditions, and high experimental throughput~\cite{cellonchip-2006,cellonchip-review,tissueonchip-2008}. In general, information on the system under study is extracted from microfluidic devices by spectroscopic techniques at the end point of the experiment. This typically involves interrogation using fluorescent probes which bind to one or a few analytes of interest. This approach can reach very high sensitivity, with limits of detection down to femtomolar concentrations. However, it is usually destructive, since the sample is affected by the addition of the marker, and can only be done once, at the end of the experiment. Following kinetic processes therefore requires using multiple samples. By contrast, NMR spectroscopy is non-invasive, generic (virtually all organic molecules give an NMR signal), and highly specific (no two metabolites share the same NMR spectrum). For these reasons, NMR spectroscopy could provide a useful complementary readout capability for microfluidic devices. For example, the metabolic activity of a cell culture sample can be followed non-invasively by NMR throughout the course of the experiment, while effects on cell differentiation can still be analysed by a (destructive) transcriptomic analysis at the end. Unfortunately, the sensitivity of NMR is much lower than that of optical techniques. The small volumes involved in microfluidic systems (typically in the range of 1 $\mu$l) compound this problem. Fortunately, the mass limit of detection of Inductive NMR detectors tends to improve as they are scaled down~\cite{Olson1995}. On this basis, a number of different micro-NMR detector designs have been proposed and characterised in the literature~\cite{utz2012review,micronmr2014review}. In most cases, these are based on micro-solenoid~\cite{SUBRAMANIAN1998,Pines2007}, planar~\cite{Maguire2007,dieter2008,EHRMANN200}, or stripline coils~\cite{stripline_jan}. While significant research has gone into developing micro-NMR detectors for flow probes, only a few designs that allow insertion of a generic microfluidic device into the detector have been described.\par
In this paper we present a novel modular probe designed for generic microfluidic-NMR experiments. The design is based on a transmission line detector~\cite{stripline_jan,gream_2016}, which is realised using inexpensive printed circuit board (PCB) technology. A modular design ensures that detectors of different geometry and size can be easily exchanged. NMR detector (including the tuning and matching circuit) is connected to the probe skeleton through detachable connectors. Modularity of the probe not only allows fast optimisation of the detector but also different detectors optimised for different experimental conditions like mass sensitivity, concentration sensitivity, sample volume, single or dual channel etc can be used on a single probe base. Using the same probe skeleton does not need any compromise of NMR sensitivity, resolution or microfluidic functionality. The cost of an additional detector is only $\sim$200 $\geneuro$ and can be manufactured within 2-3 days. The probe is designed for proton detected double resonance. The second channel can be tuned to different nuclei such as $^{13}$C, $^{15}$N, or $^{31}$P. The probe skeleton is designed entirely from easily obtainable raw materials such as aluminium profiles and tubes of standard size, with a small number of custom-machined parts holding the structure together. Detailed construction drawings for the probe are provided in the supporting information. Planer design of the detector allows to use planar exchangeable microfluidic devices. Microfluidic devices can be designed freely for specific experimental requirements as long as the overall shape of the device is maintained within l$\times$ w$\times$ t = 90mm$\times$ 20mm$\times$ 1mm.\par
In the remainder of this paper, we discuss the probe design, and characterise its performance in terms of sensitivity and resolution. We also demonstrate its application in microfluidic cell culture, protein NMR spectroscopy, and micro-imaging. Using the same probe base does not need any compromise of NMR sensitivity, resolution or microfluidic functionality.

@@

The probe assembly design is based on readily and easily available materials and parts with minimal requirement for fabrication of customised parts to avoid any bottlenecks in the building process. The probe can be built from scratch with no requirement of any part or electronics from commercial NMR probes. All the parts and electronics can be bought readily from commercial sources, with the exception of a small number of precision-machined parts which are used to hold the assembly together. These can be ordered from commercial prototyping manufacturers or machined in-house if mechanical workshop facilities are available.\par

@@

\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181015-probe-explode.png} 
\caption{Exploded view of he probe design (left) and assembled probe (right). Probe base (blue) and scaffold assembly (green) with base PCB (brown,8) makes a generic mounting point for the NMR detector (red). A microfluidic device (1) can be inserted from the top of the probe. The device sits on a spacer (4) between the detector planes (3 and 5) having the sample chamber coinciding with the constriction of the PCB planes. A modular PCB insert (6) can be exchanged to change the X channel frequency to $^{13}$C or $^{15}$N. Modular NMR detector is made up of parts 3 to 6 and is connected to the base plate PCB (8) through detachable SMP connectors. Top shows a photograph of the PCB plane 3 having stripline geometry and pads for circuit elements and SMP connectors for RF insert 6. }

@@

The skeleton of the probe consisting of a base (blue in~\ref{fig:probe-explode}) and a scaffold assembly (green in~\ref{fig:probe-explode}) made from standard aluminium profiles. The base is made from a prefabricated aluminium profile and contains the BNC connectors for RF (Radio Frequency) input. The scaffold assembly is made up of two aluminium tubes held together with precision machined parts (10). A base PCB (8) is put on the top of the probe skeleton held with the brass rods (9) for stability. The base PCB holds capacitors (7) for secondary tuning and matching of the resonator at the magnet and low-loss SMP connectors (11 in figure~\ref{fig:ProbePhoto}) to connect the rest of the probe. The probe skeleton with the base PCB serves as a generic mounting point for the NMR detector. The NMR detector is made up of two PCBs (3 and 5), a spacer between them (4) and an RF-insert (6). The PCBs (3 and 5) also carry the circuit electronics for the channel separation and primary tuning and matching of the detector. A copper or brass auxiliary disk (2) holds the PCB's together. The probe sheath (not shown here) is connected to the auxiliary disk (2) and the scaffold assembly through screws. An exchangeable microfluidic device (1) can be inserted from the top of the detector. A microfluidic device can be filled with a sample before putting it in the probe or the device can be put in the probe with some fluidic connectors attached to fill or exchange the sample in-situ. The microfluidic device sits on the spacer between the two PCB planes coinciding the sample chamber with the constriction on the detector.  RF-insert (6) can be exchanged to tune and match the probe to different frequencies at X channel. As the detector is connected to the probe base through detachable connectors, various detectors can be used on the same probe skeleton. The detectors are based on a transmission line design~\cite{gream_2016,stripline_jan}, and fabricated from easily accessible PCB materials. Use of PCB to manufacture the detector allows for easy optimisation of detector dimensions for several applications compared to other manufacturing methods. A detector can be optimised for mass sensitivity, concentration sensitivity, resolution, sample volume, single or dual channel etc for required application.\par

@@

\includegraphics[width=.8\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-both-detectors.png}

@@

Figure~\ref{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (6) for X channel. In (A) X channel could be tuned to different nuclei by exchanging 6. However, in (B) the circuitry of the RF insert (6) is manufactured on the PCB plane (5). Inclusion of the circuitry of 6 on 5 makes the design compact. Probe (A) is compatible with Varian 600 ultra shield 14.1 T magnet having an outer diameter (O.D.) of 44.45 mm including the sheath. Probe (B) has an outer diameter (O.D.) of 38 mm including the sheath and hence can be used with a narrow bore magnet. Naturally, B can also be used with wide bore magnets with spacers or gradient stack to keep the probe centred . As already mentioned, the cost and time of making a new PCB is minimal so, different detectors could be made for different X channel frequencies.\par

@@

\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-devices.png} 

@@

The circuit for a double resonance probe is based on design shown in figure~\ref{fig:circuit}. Dimensions of the detector were chosen for a $\lambda/2$ standing wave at frequency few 100s MHz higher than the proton larmor frequency. The resonator can then be tuned to desired frequency by applying additional capacitance at the resonator. For the X channel the detector is used as a load with the other circuit elements. The detector is connected to the secondary T\&M capacitors with the transmission lines on the PCB planes. As all the circuit elements are assembled on the PCB planes, the transmission lines on the PCB have lengths similar to detector. Hence transmission lines may become a part of the resonance circuit and can severely affect the probe performance. To avoid this problem a series capacitor was included with the transmission line just before the detector to adjust the impedance of transmission line to 50~$\Omega$. In this situation the detector is matched by the transmission line and secondary T\&M capacitors can be used for fine tuning and matching.\par

@@

\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180110-circuit-diagram.png}

@@

The probe circuit was compiled in KiCAD to design the PCB layout. The PCB layout was provided to beta-layout (Aarbergen Germany) and P.W. Circuits LTD (Wigston , UK) to manufacture the PCBs. Easily and inexpensively available FR4 was used for PCB manufacturing (figure~\ref{fig:ProbePhoto} A) but inhomogeneities were observed in B${_0}$ field images for this material. Rogers RO35 from rogers corporation was later used for PCBs (figure~\ref{fig:ProbePhoto} B).\par

@@

NMR experiments were performed on Varian VNMRS console on a Varian 600 ultra shield 14.1 T magnet. Spectra in figure~\ref{fig:lineshape} and \ref{fig:media-spec} were obtained with water presaturation followed by a 90$^{\circ}$ pulse. Spectrum in figure~\ref{fig:1H-nutation} was acquired with increasing the pulse length. Spectrum in figure~\ref{fig:15N-nutation} was acquired using pulse sequence described in~\cite{bax_indirect}. All the samples were purchased from commercial sources and were used without further purification.\par

@@

A double channel probe allows heteronuclear NMR experiments which are essential for many applications like protein structure determination. The current probe can be simultaneously operated at 2 frequencies. The probe has been tuned to protons and one X channel ($^{13}$C or $^{15}$N) frequencies at a time. As already explained, the X channel tuning frequency can be changed by simply exchanging an rf-insert or the complete detector. Figure~\ref{fig:tandm} shows the measured T\&M curves at different proton (600 MHz, 500 MHz) and X channel frequencies (60 MHz and 125 MHz) corresponding to the larmor frequencies of $^{15}$N and $^{13}$C at magnetic fields of 14 T and 11.7 T respectively. The measurement were performed in the pairs of 600 MHz and 60 MHz and, 500 MHz and 125 MHz. The loaded Q factors are 42, 49, 32, 36 at 600 MHz, 500 MHz, 125 MHz and, 60 MHz respectively. Channel separation is better than 15 decibels at all operating frequencies and thus sufficient to perform decoupling during experiments.\par

@@

\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180710-tandm-sameaxis.png} 

@@

$^1$H nutation diagram of water peak for a sample of 100 mM $^{15}$N-urea dissolved in water measured at 600 MHz is shown figure~\ref{fig:1H-nutation}. RF field is highly homogeneous with 810$^{\circ}$/90$^{\circ}$ ratio of more than 90\% at 600~MHz. The probe can generate 100 kHz RF-field for an input power of 100 watts both at 600 MHz and 500 MHz corresponding to RF field efficiency of 10 kHz watts$^{-1/2}$ . $^{15}$N nutation detected on protons for the same sample is shown in figure~\ref{fig:15N-nutation}. An RF field of 6 kHz at 60 MHz can be generated at 14 T for $^{15}$N and an RF field of 14 kHz at 125 MHz can be generated at 11.7 T for $^{13}$ measurements.\par

@@

\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-1-Hnutation-171216-103.png} 
\caption{$^1$H nutation acquired for water peak from a sample of 100 mM $^{15}$N-urea dissolved in water measured at 600 MHz. The 810$^{\circ}$/90$^{\circ}$ ratio is more than 90\% at 600~MHz. The 90$^{\circ}$ pulse length is below 2.5 $\mu$ sec corresponding to 100 kHz radio-frequency field for an input power of 100 Watts. Similar B$_{1}$ efficiency and homogeneity was observed at 500 MHz}

@@

\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-15-Nnutation-171215-003.png} 

@@

Figure~\ref{fig:lineshape} shows a spectrum of 130 mM Na-acetate dissolved in H$_2$O acquired after water presaturation at 600 MHz with 32 averages. The figure in the inset shows expanded view of the base of the acetate peak. Carbon satellites can be seen well above noise level. The orange curve corresponds to a lorentzian lineshape with full width at half maximum of 3.35 Hz. Limit of detection $nLOD_{\omega}=\frac{3n\sqrt{{\Delta}t}}{SNR}$ is  1.18 nmol s$^{1/2}$ at 600 MHz for the acetate sample. The measured LOD is found to be better than the calculated LOD in~\cite{gream_2016} for 600 MHz.\par

@@

\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/lineshape.png} 

@@

\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/media-180125-005-bigger-font.png} 

@@

\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-180612-HSQCspect.png} 

@@

\includegraphics[width=\linewidth,keepaspectratio=true]{./figures/ms5n17-tisli-im-180511.png} 

@@

@@

\bibliographystyle{plain}

>>>>

\title{Modular transmission line probes for microfluidic nuclear magnetic resonance spectroscopy and imaging}

@@

Microfluidic NMR (Nuclear Magnetic Resonance) can probe chemical or bio-chemical reactions, including the metabolism of cells, and tissues non-invasively in a tightly controlled and tailored microfluidic environment. We present a dual-channel modular probe assembly for  high efficiency microfluidic-NMR. The samples are contained in exchangeable, flow compatible planar microfluidic devices. The detector including the tuning and matching circuitry of the probe is modular and allows the use of different detectors optimised for different experimental conditions on the same probe base. The probe body is made from prefabricated aluminium profiles and few precision machined parts, while the probe circuit and detector are made from PCB (printed circuit borard) materials. The probe can be built from scratch with no requirement of any parts or electronics from commercial probes. The probe has a limit of detection of 1.18 nmol s$^{-1/2}$ and excellent B$_{1}$ homogeneity. The probe is optimised for proton detection and can be tuned and matched simultaneously to proton and X channel ($^{13}$C or $^{15}$N) frequencies. We have successfully acquired $^1$H-$^{13}$C and $^1$H-$^{15}$N heteronuclear correlation spectrum (HSQC). Particularly, $^1$H-$^{15}$N HSQC spectrum of 1 mM $^{15}$N labeled ubiquitin from 2.5 $\mu$l of sample volume.

@@

@@

NMR (Nuclear Magnetic Resonance) is a well established technique used in chemical analysis~\cite{NMR-chemical-1995, hills1994magnetic, rabenstein1991quantitative}, metabolomics~\cite{nmr-metabolomics-future-2017,nmr-metabolomics-2016}, molecular structure determination~\cite{wuthrich1990protein}, reaction monitoring~\cite{maiwald2004quantitative} etc. Microfluidic lab-on-a-chip (LOC) devices are increasingly finding wide applications in chemistry and the life sciences~\cite{whitesides2006origins,mark2010microfluidic}. In addition to providing a way to integrate complex chemical and biochemical analytical processes with sample preparation and even culture of cells and other biological systems, they allow detailed control over growth conditions, and offer high experimental throughput~\cite{cellonchip-2006,cellonchip-review,tissueonchip-2008}. In spite of its analytical power, NMR is rarely used in microfluidic systems. In general, information on the system under study is extracted from microfluidic devices by spectroscopic techniques at the end point of the experiment using fluorescent probes which bind to one or a few analytes of interest. This approach can reach very high sensitivity, with limits of detection down to femtomolar concentrations. However, it is usually destructive, since the sample is affected by the addition of the marker, and can only be done once, at the end of the experiment. Following kinetic processes therefore requires using multiple samples. By contrast, NMR spectroscopy is non-invasive, generic (virtually all organic molecules give an NMR signal), and highly specific (no two metabolites share the same NMR spectrum). For these reasons, NMR spectroscopy could provide a useful complementary readout capability for microfluidic devices. For example, the metabolic activity of a cell culture sample can be followed non-invasively by NMR throughout the course of the experiment, while effects on cell differentiation can still be analysed by a (destructive) transcriptomic analysis at the end. Unfortunately, the sensitivity of NMR is much lower than that of optical techniques. The small volumes involved in microfluidic systems (typically in the range of 1 $\mu$l) compound this problem. Fortunately, the mass limit of detection of inductive NMR detectors tends to improve as they are scaled down~\cite{Olson1995}. On this basis, a number of different micro-NMR detector designs have been proposed and characterised in the literature~\cite{utz2012review,micronmr2014review}. In most cases, these are based on micro-solenoid~\cite{SUBRAMANIAN1998,Pines2007}, planar~\cite{Maguire2007,dieter2008,EHRMANN200}, or stripline coils~\cite{stripline_jan}. While significant research has gone into developing micro-NMR detectors for flow probes, only a few designs that allow insertion of a generic microfluidic device into the detector have been described.\par
In this paper we present a novel modular probe designed for generic microfluidic-NMR experiments. The design is based on a transmission line detector~\cite{stripline_jan,gream_2016}, which is realised using inexpensive printed circuit board (PCB) technology. A modular design ensures that detectors of different geometry and size can be easily exchanged. The NMR detector (including the tuning and matching circuit) is connected to the probe skeleton through detachable connectors. Modularity of the probe not only allows fast optimisation of the detector but also different detectors optimised for different microfluidic device designs can be used on a single probe base. Using the same probe skeleton does not need any compromise of NMR sensitivity, resolution or microfluidic functionality. The cost of an additional detector is only $\sim$200 $\geneuro$ and can be manufactured within 2-3 days. The probe is designed for proton detected double resonance. The second channel can be tuned to different nuclei such as $^{13}$C, $^{15}$N, or $^{31}$P. The probe skeleton is designed entirely from easily obtainable raw materials such as aluminium profiles and tubes of standard size, with a small number of custom-machined parts holding the structure together. Detailed construction drawings for the probe are provided in the supporting information. Planar design of the detector allows to use planar exchangeable microfluidic devices. Microfluidic devices can be designed freely for specific experimental requirements as long as the overall shape of the device is maintained within l$\times$ w$\times$ t = 90mm$\times$ 20mm$\times$ 1mm.\par
In the remainder of this paper, we discuss the probe design in more detail, and characterise its performance in terms of sensitivity and resolution. We also demonstrate its application in microfluidic cell culture, protein NMR spectroscopy, and micro-imaging. Using the same probe base does not require any compromise of NMR sensitivity, resolution or microfluidic functionality.

@@

@@

\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181218-probe.png} 
\caption{Micrograph of the probe with and without the sleeve.}
\label{fig:probe} 
The probe assembly design is based on readily and easily available materials and parts with minimal requirement for fabrication of customised parts to avoid any bottlenecks in the building process. The probe can be built from scratch with no requirement of any part or electronics from commercial NMR probes. All parts and electronic components are readily available from commercial sources, with the exception of a small number of precision-machined parts which are used to hold the assembly together. These can be ordered from commercial prototyping manufacturers or machined in-house if mechanical workshop facilities are available.\par
\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-Probe-explode.png} 
\caption{Exploded view of he probe design (left) and assembled probe (right). Probe base (blue) and scaffold assembly (green) with base PCB (brown, 8) provides a generic mounting point for the NMR detector (red). A microfluidic device (1) can be inserted from the top of the probe. The device is held in place by a spacer (4) between the detector planes (3 and 5) assuring alignment of the sample chamber with the constriction of the PCB planes. A modular PCB insert (6) can be exchanged to change the X channel frequency to $^{13}$C or $^{15}$N. Modular NMR detector is made up of parts 3 to 6 and is connected to the base plate PCB (8) through detachable SMP connectors. Top shows a photograph of the PCB plane 3 having stripline geometry and pads for circuit elements and SMP connectors for RF insert 6. }

@@

The probe assembly can be divided into three main assemblies: A) probe base; B) scaffold assembly; C) detector assembly. The  base (blue in~\ref{fig:probe-explode}) and the scaffold assembly (green in~\ref{fig:probe-explode}) together make the skeleton of the probe. Both the base and scaffold assembly are made from standard aluminium profiles. The base contains the BNC connectors for RF (Radio Frequency) input. These BNC connectors are connected to semi-rigid coaxial cables for RF transport in the probe.\par
The scaffold assembly is made up of two hollow aluminium tubes held together with precision machined parts (scaffold support disks (10)). The semi-rigid cables are threaded through these hollow aluminium tubes to reach the detector assembly . Additional auxiliary support disks made from 5 mm PMMA are used for better stability of the scaffold assembly. A tuning and matching PCB (8) is put on the top of the probe skeleton held with the detector support rods (9) and semi-rigid coaxial cables. Both conductors of the coaxial cables are connected to the tuning and matching PCB. The tuning and matching PCB holds capacitors (7) for secondary tuning and matching of the detector and low-loss SMP connectors (11 in figure~\ref{fig:ProbePhoto}) to connect the detector assembly. Secondary tuning and matching capacitors are used for fine tuning and matching of a detector at the magnet through tuning rods. The tuning and matching PCB provides a mechanical connection between capacitors (7) and tuning rods such that the detectors tuned to very different frequencies (100s of MHz apart) can be exchanged freely without disturbing the tuning and matching capacitors (7). The base, the scaffold assembly and, the tuning and matching PCB all have a free circular axial bore providing access from the bottom of the probe. A free access from the bottom can be used for temperature and environmental control inside the probe.\par
The NMR detector is made up of two PCBs (3 and 5), a spacer between them (4) and an RF-insert (6). The detector is based on a planar transmission line geometry as described before~\cite{gream_2016,stripline_jan}. In this geometry the detector is made from a planar copper strip. The width of the copper strip is larger at the ends and smaller in the middle making a constriction. Due to smaller width the current density and hence the sensitivity increases at the constriction. Both the PCBs (3 and 5) have the constriction geometry  and also carry the circuit electronics for the channel separation and primary tuning and matching of the detector. A copper or brass auxiliary disk (2) holds the PCBs together. The probe sheath (not shown here) is connected to the auxiliary disk (2) and the scaffold assembly through screws. An exchangeable microfluidic device (1) can be inserted from the top of the detector. A microfluidic device can be filled with a sample before putting it in the probe or the device can be put in the probe with some fluidic connectors attached to fill or exchange the sample in-situ. The microfluidic device sits on the spacer between the two PCB planes coinciding the sample chamber with the constriction on the detector.  RF-insert (6) can be exchanged to tune and match the probe to different frequencies at X channel. As the detector is connected to the probe base through detachable connectors, various detectors can be used on the same probe skeleton. The detectors are fabricated from easily accessible PCB materials. Use of PCB to manufacture the detector allows for easy optimisation of detector dimensions for several applications compared to other manufacturing methods. Example of different detectors can be detectors tuned to different resonance frequencies or detectors with customised constriction geometries for different microfluidic devices.\par

@@

\includegraphics[width=.5\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-both-detectors.png}

@@

Figure~\ref{fig:ProbePhoto} shows two different versions of the probe with and without the RF insert (6) for the X channel. In (A) the X channel can be tuned to different nuclei by exchanging 6. However, in (B) the circuitry of the RF insert (6) is manufactured on the PCB plane (5). Inclusion of the circuitry of 6 on 5 makes the design more compact. Probe (A) is compatible with Varian 600 ultra shield 14.1 T magnet having an outer diameter (O.D.) of 44.45 mm including the sheath. Probe (B), with an outer diameter (O.D.) of 38 mm including the sheath, is designed to fit inside a Bruker narrow bore shim stack. Probe (B) also fits inside a Bruker micro-imaging gradient unit. Naturally, B can also be used with wide bore magnets with spacers or gradient stack to keep the probe centred .\par

@@

\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-181007-devices.png} 

@@

The circuit for a double resonance probe is based on design shown in figure~\ref{fig:circuit}. Dimensions of the detector were calculated from the simulations described in~\cite{gream_2016}. However, the size of the constriction was larger compared to~\cite{gream_2016} to allow use of larger sample volumes for some cases. The detector is tuned to proton larmor frequency of protons. Primary tuning of the detector is performed through the circuit elements. The detector is connected to the secondary tuning and matching capacitors with the transmission lines on the PCB planes. As all the circuit elements are assembled on the PCB planes, the transmission lines on the PCB have lengths similar to the detector. Hence transmission lines may become a part of the resonance circuit and can severely affect the probe performance. To avoid this problem a series capacitor was included with the transmission line just before the detector to adjust the impedance of transmission line to 50~$\Omega$. In this situation the detector is matched by the transmission line and secondary tuning and matching capacitors can be used for fine tuning and matching.\par

@@

\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180110-circuit-diagram.png}

@@

The probe circuit was compiled in KiCAD to design the PCB layout. The PCB layout was provided to beta-layout (Aarbergen Germany) and P.W. Circuits LTD (Wigston , UK) to manufacture the PCBs. Easily and inexpensively available FR4 was used for PCB manufacturing for (figure~\ref{fig:ProbePhoto} A). Rogers RO35 from rogers corporation was used for PCBs used in (figure~\ref{fig:ProbePhoto} B).\par

@@

NMR experiments were performed on Varian VNMRS console on a Varian 600 ultra shield 14.1 T magnet. Spectra in figure~\ref{fig:lineshape} and \ref{fig:media-spec} were obtained with water presaturation followed by a 90$^{\circ}$ pulse. Spectrum in figure~\ref{fig:1H-nutation} was acquired with increasing the pulse length. Spectrum in figure~\ref{fig:15N-nutation} was acquired using pulse sequence described in~\cite{bax_indirect}. Sodium acetate and $^{15}$N labeled urea were purchased from Merek and Dulbecco Modified Eagle?s Medium (DMEM) supplemented was purchased from Life Technologies, USA.\par

@@

A double channel probe allows heteronuclear NMR experiments which are essential for many applications like protein structure determination. The current probe can be simultaneously operated at 2 frequencies. The probe has been tuned to protons and one X channel ($^{13}$C or $^{15}$N) frequencies at a time. As already explained, the X channel tuning frequency can be changed by simply exchanging an rf-insert or the complete detector. Figure~\ref{fig:tandm} shows the measured tuning and matching curves at different proton (600 MHz, 500 MHz) and X channel frequencies (60 MHz and 125 MHz) corresponding to the larmor frequencies of $^{15}$N and $^{13}$C at magnetic fields of 14 T and 11.7 T respectively. The measurement were performed in the pairs of 600 MHz and 60 MHz and, 500 MHz and 125 MHz. The loaded Q factors are 42, 49, 32, 36 at 600 MHz, 500 MHz, 125 MHz and, 60 MHz respectively. Channel separation is better than 15 decibels at all operating frequencies and thus sufficient to perform decoupling during experiments.\par

@@

\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-im-180710-tandm-sameaxis.png} 

@@

$^1$H nutation diagram of water peak for a sample of 100 mM $^{15}$N-urea dissolved in water measured at 600 MHz is shown figure~\ref{fig:1H-nutation}. RF field is highly homogeneous with 810$^{\circ}$/90$^{\circ}$ ratio of more than 90\% at 600~MHz. The probe can generate 100 kHz RF-field for an input power of 100 W both at 600 MHz and 500 MHz corresponding to RF field efficiency (B$_{1}/\sqrt{power}$) of 10 kHz/$\sqrt{W}$ . $^{15}$N nutation detected on protons for the same sample is shown in figure~\ref{fig:15N-nutation}. An RF field of 6 kHz at 60 MHz can be generated at 14 T for $^{15}$N with 100 W power and an RF field of 14 kHz at 125 MHz can be generated at 11.7 T for $^{13}$C with measurements.\par

@@

\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-1-Hnutation-171216-103.png} 
\caption{$^1$H nutation acquired for water peak from a sample of 100 mM $^{15}$N-urea dissolved in water measured at 600 MHz. The 810$^{\circ}$/90$^{\circ}$ ratio is more than 90\% at 600~MHz. The 90$^{\circ}$ pulse length is below 2.5 $\mu$ sec corresponding to 100 kHz radio-frequency field for an input power of 100 W. Similar B$_{1}$ efficiency and homogeneity was observed at 500 MHz}

@@

\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-150218-15-Nnutation-171215-003.png} 

@@

Figure~\ref{fig:lineshape} shows a spectrum of 130 mM Na-acetate dissolved in H$_2$O acquired after water presaturation at 600 MHz with 32 averages. The figure in the inset shows expanded view of the base of the acetate peak. Carbon satellites can be seen well above noise level. The orange curve corresponds to a Lorentzian lineshape with full width at half maximum of 3.35 Hz. Limit of detection $nLOD_{\omega}=\frac{3n\sqrt{{\Delta}t}}{SNR}$ is  1.18 nmol s$^{1/2}$ at 600 MHz for the acetate sample. The measured LOD is found to be better than the calculated LOD in~\cite{gream_2016} for 600 MHz.\par

@@

\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/lineshape.png} 

@@

\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/media-180125-005-bigger-font.png} 

@@

\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tlp-sp-180612-HSQCspect.png} 

@@

\includegraphics[width=.7\linewidth,keepaspectratio=true]{./figures/ms5n17-tisli-im-180511.png} 

@@

Although FR4 is a cheap and quickly available material, inhomogeneities were observed in B$_0$ field images made from this PCBs. Better resolution can be achieved using Rogers RO35 from rogers corporation.

@@

\bibliographystyle{unsrt}
